SoK: Defenses Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-13 docs/questioning.tex
more corrections

  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms ({\sc c}) & {\sc xss} \\

@@

  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc s}) & {\sc xss} \\ 

@@

Table~\ref{tab:comp} shows for every mechanism its corresponding
overhead. In addition, it indicates if the overhead is applied to the
server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
percentage, while in other cases, 7 our of 34 (20.5\%), the authors
provide the time (in terms of ms) that their mechanisms add to the
normal execution time of the protecting entity. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to move from absolute
time measurements to percentage overheads. In 10 cases (29,4\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). In the case of {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.

@@

Computational overhead comes up as a non-trivial issue. We observe
that the average overhead that can be extracted from the publications
that provide the overhead in percentage terms is 18\%. Relative
research on protection mechanisms~\cite{SPWS13} indicates that
mechanisms that introduce an overhead larger than 10\% do not tend to
gain wide adoption in production environments. Hence, the
computational overhead of some mechanisms could be a reason why they
have not been adopted.

>>>>

  &   {\it WebJail}~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\

@@

  &   {\it Noncespaces}~\cite{GC09} & 109 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 

@@

Table~\ref{tab:comp} shows for every mechanism its corresponding
overhead. In addition, it indicates if the overhead is applied to the
server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
percentage, while in other cases, 7 our of 34 (20.5\%), the authors
provide the time (in terms of ms) that their mechanisms add to the
normal execution time of the protecting entity. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to move from absolute
time measurements to percentage overheads. In 10 cases (29.4\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). In the case of {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.

@@

Computational overhead comes up as a non-trivial issue. We observe
that the average overhead that can be extracted from the publications
that provide the overhead in percentage terms is 17.45\%. Relative
research on protection mechanisms~\cite{SPWS13} indicates that
mechanisms that introduce an overhead larger than 10\% do not tend to
gain wide adoption in production environments. Hence, the
computational overhead of some mechanisms could be a reason why they
have not been adopted.
